---
title: "shiny_project"
author: "Alfredo Aranda Núñez"
date: "8 de abril de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Analysis Report
This solution takes the web example about predictions of diamond's price. The main idea is to deploy solution, pull on github and publish an Rmarkdown

Diamond Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Application Overview

- Diamonds Properties can be analysed using several Parameters.
- Carat,Price,sample size,color Depth are some of the common parameters.
- This Report enables to pick the right parameters for the best Diamond selection.


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://alfred182.shinyapps.io/diamond-shiny/

Click the link below for compiled project files on gitub repo.

https://github.com/AlfredoArandan/CourseProject_c9

## Data Used
The data used for this application is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```
